%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plasmati Graduate CV
% LaTeX Template
% Version 1.0 (24/3/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati (alessandro.plasmati@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template needs to be compiled with XeLaTeX.
% The main document font is called Fontin and can be downloaded for free
% from here: http://www.exljbris.com/fontin.html
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a4paper,10pt]{extarticle} % Default font size and paper size

\usepackage{xunicode, fontspec} % For loading fonts
\defaultfontfeatures{Mapping=tex-text}
% \setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin} % Main document font
% \fontspec{[FontAwesome.otf]}
\setmainfont[Path = ./Ubuntu/,  %% Optional; but UPDATE this if 
                         %% your font files are in a folder
 Extension = .ttf,
 UprightFont = *-Regular,
 BoldFont = *-Bold,
 ItalicFont = *-Italic,
 SmallCapsFont = *-Medium]
{Ubuntu}
\fontspec{[fontawesome-webfont.ttf]}

\usepackage[usenames,dvipsnames]{xcolor} % Required for specifying custom colors
\definecolor{primary}{RGB}{130, 2, 99}
\definecolor{secondary}{RGB}{128,128,128}

\usepackage{xltxtra,url,parskip} % Formatting packages


%\usepackage[big]{layaureo} % Margin formatting of the A4 page, an alternative to layaureo can be 
%\usepackage{fullpage}
\usepackage{geometry}
\geometry{a4paper,margin=0.40cm}
%\geometry{a4paper,left=20mm, top=20mm}
 %To reduce the height of the top margin uncomment: \addtolength{\voffset}{-1.3cm}

\usepackage{hyperref} % Required for adding links	and customizing them

%\definecolor{linkcolour}{rgb}{0,0.2,0.6} % Link color
\definecolor{linkcolour}{rgb}{0.3,0.3,0.3} % Link color
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour} % Set link colors throughout the document

\usepackage{titlesec} % Used to customize the \section command
\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule] % Text formatting of sections
\titlespacing{\section}{0pt}{0pt}{0pt} % Spacing around sections

\usepackage{multicol}
\setlength{\columnsep}{0cm}

\usepackage{tabularx}

\usepackage{textcomp}

\usepackage{fontawesome}

\usepackage{setspace} % New test stuff

\usepackage{enumitem}
\setlist[description]{%
  topsep=10pt,               % space before start / after end of list
  itemsep=1pt,               % space between items
%  font={\bfseries\sffamily\color{red}}, % if colour is needed
}

\def\arraystretch{1}
\renewcommand{\baselinestretch}{1.1}

\begin{document}

\pagestyle{empty} % Removes page numbering

%\font\fb=''[cmr10]'' % Change the font of the \LaTeX command under the skills section

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------
\begin{multicols}{3}
\normalsize \faPhone\ {\href{tel:07709042759|}{\  +44-7709 042 759}}

\columnbreak

\par{\centering{\huge\textsc{\textcolor{primary}{Ekum} Jaswal}}\par} % Your name
\par{\centering\normalsize {\textsc{Beaconsfield, United Kingdom}}\hfill\par}
\columnbreak
\raggedright\hfill\normalsize \faEnvelope\ {\href{mailto:ekum.jaswal@gmail.com}{\  ekum.jaswal@gmail.com}}\\
\end{multicols}

%----------------------------------------------------------------------------------------
%	LAST UPDATED
%----------------------------------------------------------------------------------------

\vspace{-0.6cm}
\hfill {\textcolor{secondary}{\scriptsize Last updated on \today}

%----------------------------------------------------------------------------------------
%	PERSONAL STATEMENT
%----------------------------------------------------------------------------------------

\section{\textcolor{primary}{Personal Statement}}
\vspace{0.2cm}
As a Conveyancer with the largest conveyancing group in the country, I carry over 65 cases and I have gained ample communication and customer service skills, along with increased know-how of the conveyancing sphere and legal documentation. I have consistently met completion targets in 2023 and gained exceptional trust pilot reviews from clients, while also fostering professional working relationships with referrers and brokers. While I have found my current role fulfilling, I am now seeking to explore new opportunities that will allow me to apply my existing skills and  provide opportunities for professional growth and development. My ability to manage a high volume of cases and consistently meet deadlines demonstrates my strong organizational and time management skills, which will be essential for my success in any position. 
\\

\section{\textcolor{primary}{Work Experience}}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------
\begingroup % Start a group for Work Experience
\setstretch{1.2} % Set the desired line spacing within the group
\begin{tabularx}{\linewidth}{ l | X }

%----------------------------------------------------------------------------------------
%	JS Law
%----------------------------------------------------------------------------------------


\textsc{Jun '22 -} & \textbf{Conveyancer} \hfill\textit{JS Law Ltd.}\\
\textsc{Dec '23}& {- Carrying freehold, leasehold, and shared equity files to completion}\\

& {- Meeting completion deadlines in lengthy chains. To date I am within the top 10 conveyancers in the company for most completions this month. Top 10 also for conveyancers in the same capacity as myself for monthly exchanges}\\

& {- Liaising with upper management on compliance issues}\\

& {- Initiated a buddy-system for new starters who work remotely. Maintain a running Teams meeting daily where the team can communicate and provide support}\\

& {- Diligently verifying Source of Funds to comply with AML regulations}\\


& {- Providing regular updates to agents, solicitors, and clients over the phone and via email}\\


& {- Assisting other conveyancers on the team with progressing their files, taking care of files whilst team members may be on annual leave}\\


& {- As this is an online firm, I regularly assist and provide patient support to clients who struggle with online systems}\\

& {- Utilising Power BI to review my pipeline and ascertain which cases to push forward and meet targets}\\
\multicolumn{1}{c}{} \\

%----------------------------------------------------------------------------------------
%	Beaumont ABS 
%----------------------------------------------------------------------------------------

\textsc{Feb '22 -} & \textbf{Legal Assistant} \hfill\textit{Beaumont ABS Ltd.}\\
\textsc{May '22}& {- Diligently conducting ID checks on clients and donors. Subsequently communicating with clients and donors where additional identification documents may be required}\\

& {- Experience ordering searches using Searchflow. I have also started to work on Search Reports.}\\

& {- Requesting redemption statements and submitting Certificates of Title – frequently using LMS and Lender Exchange for these. Proactively communicating with lenders to confirm mortgage funds will be released, in order that there are no delays on the day of completion. I have started to work on Mortgage Reports}\\

& {- Raising bills upon exchange of contracts and Completion Packs in a timely manner}\\

& {- Obtaining Official Copies from the Land Registry website and Conducting pre-completion searches (OS1 and K17)}\\

& {- Drafting Contract Packs}\\
\multicolumn{1}{c}{} \\

%----------------------------------------------------------------------------------------
%	ASDA
%----------------------------------------------------------------------------------------

\textsc{Jul '19 -} & \textbf{Store Assistant} \hfill\textit{ASDA Stores Ltd.}\\
\textsc{Sep '19}& {- Efficiently unloaded deliveries and sorted stock for several departments in the store}\\

& {- Replenished stock on the shop floor in a timely manner, thus allowing me to assist colleagues with their respective tasks}\\

& {- Provided customer service through identifying individual needs and offering insight into product queries}\\

& {- Effectively communicated with non-English speaking customers (in Punjabi and Spanish)}\\
\multicolumn{1}{c}{} \\

%----------------------------------------------------------------------------------------
%	Reynolds Porter Chamberlain
%----------------------------------------------------------------------------------------
\textsc{Oct '17 -} & \textbf{Intern}\hfill\textit{Reynolds Porter Chamberlain}\\
\textsc{Oct '17}& {- Undertook work experience at RPC, shadowing a solicitor. Worked with the Construction \& Projects team on a case undergoing adjudication, organising and selecting emails relevant to the case}\\

& {- Prepared detailed witness statements to support a case whilst on a witness call}\\

\multicolumn{1}{c}{} \\

%----------------------------------------------------------------------------------------
%	Oxfam
%----------------------------------------------------------------------------------------
\textsc{Sep '15 -} & \textbf{Volunteer}\hfill\textit{Oxfam}\\
\textsc{Aug '18}& {- Sorted donations and selected products to be sold in the shop}\\

& {-	 Accurately priced items to be sold}\\

& {-	 Trained a new volunteer in sorting and pricing}\\

& {- Cashier work, undertaking transactions during busy hours}\\

\multicolumn{1}{c}{} \\


\end{tabularx}
\endgroup % End the group

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{\textcolor{primary}{Education}}
\begin{tabular}{r|p{17.5cm}}	
2018-2021 & Bachelor of Laws (LLB) in \textbf{Law with Spanish Law}\hfill
\textbf{The University of Sheffield}\\
&\textsc{Award}: First Class Honours\\

&\textsc{Modules}: Advanced Land Law \textsc{(65\%)}, Employment Law \textsc{(75\%)}, and Intellectual Property Law \textsc{(75\%)}\\

%&\textbf{Coursework: }{Programming and Data Structures, Algorithms-I \& II, Software Engineering, Compilers, Switching Circuits, Operating Systems, Computer Networks, Information Retrieval, Database Management Systems, Theory of Computation, Machine Learning, Image Processing, Advanced Graph Theory}
\\

2016-2018 & \underline{A-Levels:}\hfill
\textbf{Beaconsfield High School}\\
& Spanish \textsc{(A)}, Mathematics \textsc{(B)}, Philosophy \textsc{(C)}, EPQ \textsc{(B)}\\
\\

2011-2016 & \underline{GCSEs:}\hfill
\textbf{Upton Court Grammar School}\\
& 4 A*s, 3 As and 4 Bs, including Maths and English\\
\end{tabular}
\\

%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------

\section{\textcolor{primary}{Projects}}
\vspace{0.1cm}
\begin{description}
\sloppy
\item[Human Rights Oral Advocacy (2020)]\hfill \\
A project which involved researching a contemporary human rights issue and giving a timed advocacy speech to a fictitious "Human Rights Council", in front of an audience of 70 people. NGO reports were used to research and draw conclusions about human rights issues in Bangladesh and the United States. I then offered practical solutions to resolve these issues

\item[Internal Mooting Competition (2019)]\hfill \\
An internal moot at the University of Sheffield, where we worked in teams on a contract dispute. I used Westlaw research cases and find authorities for my argument. I formulated a concise argument and gave a timed, five-minute, oral submission

\end{description}

%----------------------------------------------------------------------------------------
%	Positions of Responsibility
%----------------------------------------------------------------------------------------

\section{\textcolor{primary}{Positions of Responsibility}}
\vspace{0.1cm}
\begin{description}
\sloppy
\item[BME Representative of LGBT+ Society, University of Sheffield (2020-2021)]\hfill \\
Ensured there was QTIPOC (Queer, Trans and Intersex People of Colour) representation in committee meetings by actively listening and responding to society members’ suggestions and opinions

Led and organised QTIPOC socials and discussion events. For example, starting a weekly film/TV night where members could virtually watch a LGBTQ+ film or series episode together and socialise afterwards

\item[Philosophy and Ethics Forum (2017-2018)]\hfill \\
Started a forum within sixth form. Proactively brought students to participate in discussions about contemporary issues relating to teenagers and the underlying philosophical and ethical implications

Increased engagement through announcements and posters around the school

\item[Spanish Key Stage 4 Mentor (2017-2018)]\hfill \\
Mentoring for multiple students in GCSE level Spanish

Simplifying complex sentence structures and providing rules for regular and irregular verb conjugations. These methods resulted in an increase of quiz scores

\item[Sports Captain (2011-2016)]\hfill \\
Fostering a team identity with a diverse group of athletes through leading warm-up exercises

Assigning track and field positions to athletes when attending school competitions

\end{description}

\centering\textsc{References available upon request}

\end{document}

